\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2021-01-15 icra-2021.tex
added the plot with coefficients
added the edata with the time evolution of the model

\begin{figure*}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,7)
        {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
    \node[inner sep=0pt] () at (0,0)
        {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
    \node[inner sep=0pt] () at (7.9,0)
        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
  \end{tikzpicture}
  \caption{.}
\end{figure*}

>>>>

\begin{figure*}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (-1,7)
        {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
      \node[inner sep=0pt] () at (4.8,7)
        {\footnotesize\input{\figpath/results/evol_sim3.tikz}};
    \node[inner sep=0pt] () at (9.3,7)
        {\footnotesize\input{\figpath/results/coef_sim3D.tikz}};
    \node[inner sep=0pt] () at (0,0)
        {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
    \node[inner sep=0pt] () at (7.9,0)
        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
  \end{tikzpicture}
  \caption{.}
\end{figure*}
